%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template was originally downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
% Alternatively, if you use a distribution like TeX Live, ensure that
% moderncv.cls and .sty files are installed through your package manager.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10.5pt,letterpaper,sans]{moderncv} 

\moderncvstyle{classic} % CV theme
% - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{yaleblue} % CV color
% - options include: 'blue' (default), 'orange',
% 'green', 'red', 'purple', 'grey' and 'black'

\usepackage[scale=0.84]{geometry} % Reduce document margins

%% Configure fonts
\usepackage{fontspec}
% Define fonts
\newfontfamily\bitter[Path=fonts/Bitter/, Ligatures=TeX]{Bitter-Regular}
\newfontfamily\raleway[Path=fonts/Raleway/, Ligatures=TeX]{Raleway-Regular}
% Set global font
\setsansfont[Path=fonts/Raleway/,
    BoldFont=Raleway-Bold,
    ItalicFont=Raleway-Italic,
    BoldItalicFont=Raleway-BoldItalic,
    Ligatures=TeX]{Raleway-Regular}
% Set fonts by section
\renewcommand*{\namefont}{\bitter\fontsize{34}{36}\mdseries\upshape}
\renewcommand*{\titlefont}{\bitter\LARGE\mdseries\slshape}
\renewcommand*{\addressfont}{\bitter\small\mdseries\slshape}
\renewcommand*{\quotefont}{\bitter\large\slshape}
\renewcommand*{\sectionfont}{\bitter\Large\mdseries\upshape}
\renewcommand*{\subsectionfont}{\bitter\large\mdseries\upshape}

% Set Dates column width
\setlength{\hintscolumnwidth}{2.8cm} 

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Addison} 
\familyname{Hu}

% \title{}
\iffalse
\address{
    Department of Statistics \& Data Science\\
    Baker Hall\\
    Carnegie Mellon University\\
}{Pittsburgh, PA 15213}
\fi
% \mobile{(626) 703 - 9110}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\email{mail@huisaddison.com}
%\homepage{huisaddison.com} 
%\extrainfo{additional information}
%\photo[70pt][0.4pt]{picture} % The first bracket is the picture height,
%the second is %he thickness of the frame around the picture (0pt for no frame)
%\quote{
% Seeking a Job Opportunity or a PhD Placement by the 10th of September - 23
% years old} 
%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\vspace{-1cm}
\section{Education}

\cventry{\hspace{-0.4cm}August 2018 --\\ \hspace{-0.4cm}December 2023}{Carnegie Mellon University}{Pittsburgh, PA}{}{}{
    - PhD, Department of Statistics and Machine Learning Department (joint)\\
    - Thesis: Estimation of $\mathrm{BV}^k$ functions from scattered data.
}
\cventry{\hspace{-0.4cm}July 2022 --\\ \hspace{-0.4cm}December 2023}{University of California, Berkeley}{Berkeley, CA}{}{}{
    - Visiting Researcher, Department of Statistics 
}
\cventry{August 2013 -- May 2017}{Yale University}{New Haven, CT}{}{}{
    - BSc, Statistics; Distinction in Major; magna cum laude\\ 
    - Thesis: Minimax estimation of bandable precision matrices.
}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Work Experience}
\cventry{September 2024 -- present}{Senior Scientist, Performance Prediction}{Latitude AI}{Palo Alto, CA}{}{
    - Responsible for end-to-end framework integrating on-road and simulation-based data to evaluate the performance of the AV software.  This framework accelerates the development process and has been used to land new features across Perception, Prediction, and Motion Planning.
    \\
    - Data-driven human-alignment of comfort and safety metrics.  This work continually re-calibrates company metrics using machine learned models to be more consistent with demonstrated human preferences for ride behavior.
    \\
    - Consults across company on statistical inference and uncertainty quantification, in particular for safety-critical rare event estimation problems.
}
\cventry{January 2024 -- August 2024}{Visiting Scientist, Learned Autonomy Behavior}{Latitude AI}{Palo Alto, CA}{}{
    - In this postdoc-style role, I created a methodology for predicting safety and comfort metrics for new software releases by leveraging fleet and simulation-based data, with additional work on variance reduction and confidence set calibration.
    \\
}
\cventry{August 2018 -- Decemeber 2023}{Graduate Student Researcher}{Carnegie Mellon University \& UC Berkeley}{}{}{
    - \emph{Foundational work in Stat/ML theory:} my main thesis work explored the fundamental limits of estimation in bounded variation and bounded gradient variation function spaces, with estimators to achieve those limits.
    \\
    - \emph{Computational epidemiology:} motivated by the COVID pandemic, I developed forecast methodology for COVID and influenza, as part of CMU's Delphi group.  Our 2021--2022 flu season forecasts had the highest performance amongst those submitted to the CDC.
    \\
    - \emph{Atmospheric science:} I devised a spatio-temporal method for estimating subsurface ocean thermal response to tropical cyclones.  This method has been used and extended by atmospheric scientists.
    \\
}
\cventry{July 2017 -- August 2018}{Data Scientist (L3, L4), Search Core Relevance}{Facebook}{Seattle, WA}{}{
    - Worked with a machine learning engineering team, with a
      particular focus on surfacing posts previously seen by a user in high-intent
      searches (``needle searches'').
    \\
    - Designed and implemented a framework for measuring success over high-intent searches,
      including: analyses for identifying share of searches that were potential
      ``needle searches''; failure modality identification for users with high-intent
      searches; smoke tests for the content retrieval and ranking systems through
      simulated searches.
    \\
    - Mentored other data scientists and participated in statistics reading groups.  Promoted within the first year with a rating of GE.
    \\
}


%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------
\section{Papers}
\cventry{2025}{Jeremy Goldwasser, Addison J Hu, Alyssa Bilinski, Daniel J McDonald, Ryan J Tibshirani}{
  Estimating time-varying epidemic severity rates with adaptive deconvolution}{
  Submitted}{}{}
\cventry{2024}{Jeremy Goldwasser, Addison J Hu, Alyssa Bilinski, Daniel J McDonald, Ryan J Tibshirani}{
  Challenges in estimating time-varying epidemic severity rates from aggregate data}{
  Submitted}{}{}
\cventry{2024}{Sarabeth Mathis, et al}{
  Evaluation of FluSight influenza forecasting in the 2021-22 and 2022-23 seasons with a new target laboratory-confirmed influenza hospitalizations}{
  Nature Communications}{}{}
\cventry{2022}{
  Addison J Hu, Alden Green, and Ryan J Tibshirani}{
  The Voronoigram: Minimax estimation of bounded variation functions from scattered data}{
  Submitted}{}{}
\cventry{2021}{
  Veeranjaneyulu Sadhanala, Yu-Xiang Wang, Addison J Hu, and Ryan J Tibshirani}{
  Multivariate trend filtering for lattice data}{
  Annals of Statistics}{}{}
\cventry{2021}{Daniel J McDonald, Jacob Bien, Alden Green, Addison J Hu, [nine more authors]}{
  Can auxiliary indicators improve COVID-19 forecasting and hotspot prediction?}{
  Proceedings of the National Academy of Sciences}{}{}
\cventry{2021}{Alex Reinhart, et al}{
  An open repository of real-time COVID-19 indicators}{
  Proceedings of the National Academy of Sciences}{}{}
\cventry{2021}{Estee Y Cramer, et al}{
  Evaluation of individual and ensemble probabilistic forecasts of COVID-19 mortality in the US}{
  Proceedings of the National Academy of Sciences}{}{}
\cventry{2020}{
  Addison J Hu, Mikael Kuusela, Ann B Lee, Donata Giglio, and Kimberly M
  Wood}{
  Spatio-temporal methods for estimating subsurface ocean thermal response to
  tropical cyclones}{
  Advances in Statistical Climatology, Meteorology and Oceanography}{}{}
\cventry{2017}{Addison J Hu and Sahand N Negahban}{Minimax estimation of bandable
    precision matrices}{Advances in Neural Information Processing Systems}{}{}

%----------------------------------------------------------------------------------------
%   AWARDS SECTION	
%----------------------------------------------------------------------------------------
\section{Awards}
\cventry{Spring 2020}{NSF Graduate Research Fellowship Program}{}{}{}{
    - My graduate study was funded by a grant from the NSF to
    study multivariate extensions of trend filtering for scattered data.
    The research conducted under this grant culminated in my dissertation.
}

%\newpage
\iffalse
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Teaching Experience}
\cventry{Fall 2018 -- Spring 2020}{Teaching Assistant}{Carnegie Mellon University}{Pittsburgh, PA}{}{
    - Topics covered: probability theory, inference, linear models, scientific
    communication \& report writing.\\
    - Lectured in lieu of instructor when necessary.\\
    - Beginning Fall 2020, I have been relieved from teaching by an NSF GRFP 
      grant.
}

\cventry{January 2016 -- May 2017}{Teaching Fellow}{Yale Depts of Computer Science; Statistics}{New Haven, CT}{}{
    - Topics covered: 
    inference, model selection, optimization, dimensionality
    reduction, dictionary learning, matrix factorization, etc., with
    applications in R, Python, and Spark.
    \\
    \iffalse
    - Held office hours for STAT 230, an introduction to the R
    statistical language through applications in inference, simulation, model
    selection, $k$-means, PCA, and other methods.  
    \\
    - Serving in a teaching and grading role for `Computational Tools for Data
    Science', covering optimization, dimensionality reduction, clustering, 
    dictionary learning, matrix factorization, large-scale data, etc., with
    applications in Python and Spark.
    \\
    - Provided supplementary instruction for `Introduction to Information
    Systems', taught in R and Python \\ 
    \fi
}
\fi


%----------------------------------------------------------------------------------------
%	VOLUNTEER EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
%\section{Service, Professional}
\section{Service}
\cventry{2021 -- 2023}{Referee}{Annals of Statistics, Journal of Machine
  Learning Research, Journal of Computational and Graphical Statistics}{}{}{}
\cventry{\hspace{-0.2cm}2019, 2020, 2021}{Reviewer}{Neural Information Processing Systems}{}{}{
  - Top reviewer: 2019, 2020.
}
\cventry{2020 -- 2023}{Wellness Committee}{CMU Department of Statistics}{Pittsburgh, PA}{}{
    - Organized discussions, events, and other opportunities to promote holistic
    student wellness.
    }


\iffalse
\section{Service, Community}
\cventry{\hspace{-0.5cm}September 2017 -- June 2018}{Tutor}{Youth Tutoring Program}{Seattle, WA}{}{
    -- Tutoring \& mentoring for Seattle-area students from low- and
    mixed-income housing.  
}
\cventry{August 2013 -- May 2014}{Math Coach}{MathCounts Outreach}{New Haven, CT}{}{
    -- Afterschool mathematics coaching to students in the New Haven
    public school system.  
}
\cventry{August 2013 -- May 2014}{English Tutor}{Bridges ESL}{New Haven, CT}{}{
    -- English as a second language classes for members of the New Haven immigrant
    community.
}
\fi


%----------------------------------------------------------------------------------------
%	HONORS AND AWARDS SECTION
%----------------------------------------------------------------------------------------
%\bigskip

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\cvitem{}{Python, PyTorch, C++, R, \LaTeX, SQL}


%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage

%\recipient{HR Departmnet}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

%\makelettertitle % Print letter title

%\lipsum[1-3] % Dummy text

%\makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}
